# Data

```{r, include = FALSE}
library(tidyverse)
library(redav)
library(knitr)
library(mi)
```


## Technical description

This paper utilizes data from multiple sources. The first raw dataset, named 'ev_charging_stations_parsed.csv' comprises 191,514 rows and 13 columns with 191,514 rows and 12 columns after initial processing. It furnishes details about the operating organization, address of charging stations, types of charging stations, charging capacities, and more, pertaining to electric vehicle charging stations nationwide in South Korea. This dataset is sourced from the Korea Environment Corporation, a governmental entity under the Ministry of Environment of South Korea. The data was last updated on August 23, 2023, with an unknown update frequency. The format of the data is all charcters, except for the ID column which is numeric.

The second raw dataset, 'gas_stations_seoul_parsed.csv' contains 1,903 rows and 6 columns, offering information about the change in petroleum sales permit status of gas stations situated in Seoul, South Korea. This dataset is compiled by the Seoul Metropolitan Government and was last updated on November 11, 2023, with an unknown update frequency. The format of the data is all charcters, except for the "License.date" and "Date.of.closure" columns which are date columns.

The methods employed for data collection remain undisclosed. Since both datasets are in Korean, we plan to utilize either the OpenAPI or GoogleTranslateAPI to translate and preprocess the datasets in Python. This preprocessing involves parsing addresses to extract longitude and latitude coordinates, filtering of columns only necessary for our analysis and encoding categorical columns. Filtering and encoding may be done in R.

To access the first dataset, follow this link: 

<https://www.data.go.kr/data/15119741/fileData.do>

and click on, '다운로드' to download the dataset

To access the second dataset, follow this link: 

<https://data.seoul.go.kr/dataList/OA-16110/S/1/datasetView.do>

and click on, '내려받기(csv)' to download the dataset

## Research plan

We will initially assess the relative accessibility of electric vehicle (EV) charging stations in comparison to gas stations. This examination will involve analyzing the density and distribution of both types of fueling infrastructure. Our analysis will take into account factors such as the number of charging ports, charging speed, and the consistent operational status of the stations. This approach aims to provide insights into the practicality and convenience of using electric vehicles in Seoul.

Subsequently, even though historical data for EV infrastructure is unavailable, we possess historical data for gas stations. This data will be utilized for a longitudinal analysis to uncover trends in accessibility over time. By examining the annual count of operating gas stations, we can discern whether accessibility has improved, worsened, or remained relatively constant throughout the years for gas cars. This information can be utilized to make inferences about the accessibility of EV infrastructure.

## Missing value analysis
Due to limited space, only columns with a missing value count greater than 0 are included for the bar plots.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
ev <- read.csv('data/ev_charging_stations_parsed.csv')
gas <- read.csv('data/gas_stations_seoul_parsed.csv')

ev <- ev %>%
  mutate(across(where(is.character), ~ na_if(.,"")))

ev.new.names <- c("City", "Dist.", "Add.", "Name", "FC.L", "FC.S", "M.L", "M.S", "OI.L", "OI.S", "RCA", "Type", "ID")
ev.name.map <- data.frame(rbind(Previous = colnames(ev), New = ev.new.names))
kable(ev.name.map, col.names = NULL, caption = "New Column Names for EV Dataset")

colnames(ev) <- ev.new.names

# remove duplicate
ev <- ev %>% select(-RCA)

na_count_ev <-sapply(ev, function(y) sum(length(which(is.na(y))))) %>% 
  as.data.frame() %>%
  mutate(Dataset = 1) %>%
  rownames_to_column()

colnames(na_count_ev) <- c('Column', 'Null_count', 'Dataset')

ggplot(na_count_ev %>% dplyr::filter(Null_count > 0), 
       aes(x = Column, y = Null_count, label = Null_count)) +
  geom_col(stat = "identity") +
  geom_label(data = na_count_ev %>% dplyr::filter(Null_count > 0), vjust = 0.5) + 
  labs(x = "Column Name", y = "Missing Value Count", main = "Missing Value Count for EV Dataset") 
plot_missing(ev)
```
The EV dataset has 284 missing entries in the District column. However, this district information can be inferred from the address column in the dataset and address column does not have any missing entry. As a result, there is no visible pattern shown in the 'plot_missing' plot.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
gas <- gas %>%
  mutate(across(where(is.character), ~ na_if(.,"")))

gas <- gas %>% 
  mutate(License.date = lubridate::ymd(License.date)) %>%
  arrange(License.date)

gas.new.names <- c("Status", "Add.", "SNAdd.", "BN", "LD", "DoC")
gas.name.map <- data.frame(rbind(Previous = colnames(gas), New = gas.new.names))
kable(ev.name.map, col.names = NULL, caption = "New Column Names for EV Dataset")

colnames(gas) <- gas.new.names

na_count_gas <-sapply(gas, function(y) sum(length(which(is.na(y))))) %>%
  as.data.frame() %>%
  mutate(Dataset = 1) %>%
  rownames_to_column()

colnames(na_count_gas) <- c('Column', 'Null_count', 'Dataset')

ggplot(na_count_gas %>% dplyr::filter(Null_count > 0), 
       aes(x = Column, y = Null_count, label = Null_count)) +
  geom_col(stat = "identity") +
  geom_label(data = na_count_gas %>% dplyr::filter(Null_count > 0), vjust = 0.5) + 
  labs(x = "Column Name", y = "Missing Value Count", main = "Missing Value Count for Gas Dataset")

plot_missing(gas)

#gas %>% filter(is.na(DoC)) %>% group_by(Status) %>% summarise( n = n())

#gas %>% filter(is.na(DoC), Status == "폐업") 

# gas <- gas %>% mutate(yearOpened = lubridate::year(LD)) %>%
#   group_by(yearOpened) %>%
#   filter(is.na(DoC)) %>%
#   summarise(n = n())
# 
# ggplot(gas, aes(x = yearOpened, y = n)) +
#   geom_line()
```
The dataframe has been ordered by the License.Date, the date of which the petroleum sales permit was given. 

To provide a brief context, Korea implemented Western-style street name addresses (SDAdd.) in 2014, replacing the standard address system denoted by Add.

If a gas station closed before 2014, it may lack a street name address since the data for such stations is no longer being tracked. However, address information can be converted to street name addresses, and vice versa. A closer examination of entries missing the address column reveals that street name addresses are available and there is no entry where both the address column and street name address column are missing, ensuring no loss of data. 

Gas stations still in operation will not have a Date of Closure. Upon closer inspection, out of 1200 missing data entries, 563 gas stations are not currently operating with no Date of Closure. Most of these gas stations were licensed in the late 20th century, suggesting that these data might have been lost due to administrative issues. However, as we will only be using data from the last decade (since EVs were introduced only a decade ago), this loss will not impact our analysis. We observe from the 'plot_missing' plot, as expected, that some businesses that opened before 2014 have missing SNAdd. (Street Name Address), while businesses that opened in recent years have missing Add. (Address).

Thus, our data does not contain any missing value that may hinder our analysis.
